Enhancement of SDR in Thessaloniki

### 2024-04-10 high_aod/GHI_enh_03_process.tex
Commit 2024-04-10 12:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-08}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}

 USING CSMODE: Low_B.Low_W

C4 factor: 1.05 
C4 offset: 0 
\end{verbatim}

\FloatBarrier

## Days with extreme cases day 
\end{verbatim}

\FloatBarrier

## Days with strong enhancement day 
\end{verbatim}

\FloatBarrier

## Days with sunny day 
\end{verbatim}

\FloatBarrier

## Days with sunny enhancement day 
\end{verbatim}

\FloatBarrier

## Days with cloudy day 
\end{verbatim}

\FloatBarrier

## Days with random day 
\end{verbatim}

\FloatBarrier

## Days with manual test days 
\end{verbatim}

\begin{verbatim}
Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2 3.5.0.
i Please use the `legend.position.inside` argument of `theme()` instead.
This warning is displayed once every 8 hours.
Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
\end{verbatim}

\begin{verbatim}
2024-04-08 15:48:57.0 athan@sagan GHI_enh_02_ID_CE.R 29.123272 mins
\end{verbatim}

Alpha * HAU is CS\_ref

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-372.77 -150.51  -49.67   99.05  778.55

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)      -9.118e+01  5.082e+01  -1.794   0.0736 .  
as.numeric(Date)  3.246e-07  4.062e-08   7.991 1.82e-14 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 217 on 361 degrees of freedom
Multiple R-squared:  0.1503,    Adjusted R-squared:  0.148 
F-statistic: 63.86 on 1 and 361 DF,  p-value: 1.815e-14
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-372.77 -150.51  -49.67   99.05  778.55

Coefficients:
                    Estimate Std. Error t value Pr(>|t|)    
(Intercept)       -9.118e+01  5.082e+01  -1.794   0.0736 .  
ST_E_monthly$Date  3.246e-07  4.062e-08   7.991 1.82e-14 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 217 on 361 degrees of freedom
Multiple R-squared:  0.1503,    Adjusted R-squared:  0.148 
F-statistic: 63.86 on 1 and 361 DF,  p-value: 1.815e-14
\end{verbatim}

@@

\begin{verbatim}
aa
aday
All_daily_ratio_lim
alpha
ampl
avar
BIO_ELEVA
C1_Clearness_Kt_THRES
C1_GLB_diff_THRES
C2_Clearness_Kt_THRES
C3_cs_ref_ratio
C4_cs_ref_ratio
C4_GLB_diff_THRES
C4_lowcut_ratio
C4_lowcut_sza
Clear_daily_ratio_lim
CLEARdir
Cloud_daily_ratio_lim
cols
common_data_13
common_data_14
common_data_14_2
CS_file_13
CS_file_14
CS_file_14_2
csmodel
Daily_aggregation_N_lim
Daily_confidence_limit
daylist
Days_of_year
dummy
Energy_Div
I1_longterm
I2_szatrend
I3_trendsconsist
ii
Input_data_ID
Kurudz_SC
MIN_ELEVA
MIN_N
Monthly_aggegation_N_lim
Monthly_confidence_limit
my.cols
my.cols.gr
pyear
R_COMPILE_PKGS
RANDOM_SEED
raw_input_data
running_mean_window_days
running_mean_window_years
SEAS_MIN_N
SelEnhanc
SZA_aggregation_N_lim
SZA_BIN
SZA_confidence_limit
variables_fl
yearstodo
ylim
ST_daily
ST_E_daily
ST_E_daily_seas
ST_E_monthly
ST_E_monthly_seas
ST_E_sza
ST_E_sza_doy
ST_E_sza_monthly
ST_E_yearly
ST_extreme_daily
ST_extreme_monthly
ST_extreme_SZA
ST_extreme_SZA_doy
ST_extreme_SZA_monthly
ST_extreme_total
ST_extreme_yearly
ST_G0
ST_G1
ST_monthly
ST_sza
ST_sza_doy
ST_sza_monthly
ST_total
ST_yearly
\end{verbatim}

@@

\begin{verbatim}
2024-04-08 15:55:25.5 athan@sagan GHI_enh_02_ID_CE.R 3.671820 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-09}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
Alpha * HAU is CS\_ref

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-1440.3  -533.0  -125.8   463.6  2804.6

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)      -2.647e+02  1.691e+02  -1.565    0.118    
as.numeric(Date)  1.153e-06  1.354e-07   8.517 4.38e-16 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 728.2 on 364 degrees of freedom
Multiple R-squared:  0.1662,    Adjusted R-squared:  0.1639 
F-statistic: 72.54 on 1 and 364 DF,  p-value: 4.375e-16
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-1440.3  -533.0  -125.8   463.6  2804.6

Coefficients:
                    Estimate Std. Error t value Pr(>|t|)    
(Intercept)       -2.647e+02  1.691e+02  -1.565    0.118    
ST_E_monthly$Date  1.153e-06  1.354e-07   8.517 4.38e-16 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 728.2 on 364 degrees of freedom
Multiple R-squared:  0.1662,    Adjusted R-squared:  0.1639 
F-statistic: 72.54 on 1 and 364 DF,  p-value: 4.375e-16
\end{verbatim}

@@

\begin{verbatim}
aa
aday
All_daily_ratio_lim
alpha
ampl
avar
BIO_ELEVA
C1_Clearness_Kt_THRES
C1_GLB_diff_THRES
C2_Clearness_Kt_THRES
C3_cs_ref_ratio
C4_cs_ref_ratio
C4_GLB_diff_THRES
C4_lowcut_ratio
C4_lowcut_sza
Clear_daily_ratio_lim
CLEARdir
Cloud_daily_ratio_lim
cols
common_data_13
common_data_14
common_data_14_2
CS_file_13
CS_file_14
CS_file_14_2
csmodel
Daily_aggregation_N_lim
Daily_confidence_limit
daylist
Days_of_year
Energy_Div
I1_longterm
I2_szatrend
I3_trendsconsist
ii
Input_data_ID
Kurudz_SC
MIN_ELEVA
MIN_N
Monthly_aggegation_N_lim
Monthly_confidence_limit
my.cols
my.cols.gr
pyear
R_COMPILE_PKGS
RANDOM_SEED
raw_input_data
running_mean_window_days
running_mean_window_years
SEAS_MIN_N
SelEnhanc
SZA_aggregation_N_lim
SZA_BIN
SZA_confidence_limit
variables_fl
yearstodo
ylim
ST_daily
ST_E_daily
ST_E_daily_seas
ST_E_monthly
ST_E_monthly_seas
ST_E_sza
ST_E_sza_doy
ST_E_sza_monthly
ST_E_yearly
ST_extreme_daily
ST_extreme_monthly
ST_extreme_SZA
ST_extreme_SZA_doy
ST_extreme_SZA_monthly
ST_extreme_total
ST_extreme_yearly
ST_G0
ST_G1
ST_monthly
ST_sza
ST_sza_doy
ST_sza_monthly
ST_total
ST_yearly
\end{verbatim}

@@

\begin{verbatim}
2024-04-09 20:39:01 athan@tyler GHI_enh_03_process.R 13.754702 mins
\end{verbatim}

### 2024-04-10 high_aod/GHI_enh_06_sza.tex
Commit 2024-04-10 12:14

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
Not changed:  ./GHI_enh_06_sza.R 
Not changed:  ./GHI_enh_00_variables.R 
Not changed:  ./GHI_enh_03_process.R 
Not changed:  ./data/GHI_enh_03_process.Rda 
\end{verbatim}

\begin{verbatim}
[1] FALSE
\end{verbatim}

\begin{verbatim}
Written `R_make_` file: .//.R_make.mk 
\end{verbatim}

@@

\begin{verbatim}
2024-03-14 19:08:05.8 athan@tyler GHI_enh_06_sza.R 0.401094 mins
\end{verbatim}

>>>>

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\newpage
\FloatBarrier

@@

\begin{verbatim}
2024-03-14 19:41:18.5 athan@tyler GHI_enh_06_sza.R 0.846766 mins
\end{verbatim}
